---
title: "Assignment #9: Part II"
author: "Learning Group 3:Meka McCammon, Joy Li, Anna Ehrhorn, and Genee’ Glascoe"
date: "April 11, 2020"
output: html_notebook
---

***
This is a study investigated the following research question: *For women who* 
*suffered childhood physical abuse, is a difference in the average PTSD scores* 
*of women who also suffered childhood sexual abuse and those who did not suffer* 
*childhood sexual abuse, after accounting for the severity of the childhood*
*physical abuse?*

```{r include=FALSE}

library(tidyverse)

abuse.data <- read_csv("Sexual Abuse Data.csv")

abuse.data

abuse.data$csa <- factor(abuse.data$csa,
                         levels = c("Abused", "NotAbused"),
                         labels = c("Abused", "Not Abused"))
```


***
### Question 1 
#### These are boxplots that show differences in average PTSD scores of women who suffered  childhood sexual abuse compared to those who did not suffer from childhood sexual abuse after accounting for the severity of the childhood physical abuse 
```{r echo=FALSE}
ggplot(abuse.data, aes(x = csa, y = ptsd)) +
  geom_boxplot()+
  stat_summary(fun = "mean", color = "red", size = 1.5, geom = "point")+
  labs(x = "Childhood Sexual Abuse",
       y = "PTSD Score",
       title = "Relationship of PTSD Scores of Sexually Abused and Not Abused Women")
```


***
### Question 2
#### Assigned to Genee'


***
### Question 3
#### Assigned to Anna


***
### Question 4
#### Assigned to Joy


***
### Question 5
#### Assigned to Meka


***
### Question 6
#### Assigned to Genee'


***
### Question 7
#### Assigned to Anna


***
### Question 8
#### Assigned to Joy


***
### Question 9
#### Assigned to Joy

