---
title: "Assignment #9: Part II"
author: "Learning Group 3:Meka McCammon, Joy Li, Anna Ehrhorn, and Genee’ Glascoe"
date: "April 11, 2020"
output: html_notebook
---

***
This is a study investigated the following research question: *For women who* 
*suffered childhood physical abuse, is a difference in the average PTSD scores* 
*of women who also suffered childhood sexual abuse and those who did not suffer* 
*childhood sexual abuse, after accounting for the severity of the childhood*
*physical abuse?*

```{r include=FALSE}

library(tidyverse)

abuse.data <- read_csv("Sexual Abuse Data.csv")

abuse.data

abuse.data$csa <- factor(abuse.data$csa,
                         levels = c("Abused", "NotAbused"),
                         labels = c("Abused", "Not Abused"))
```


***
### Question 1 

Side-by-side boxplots that show differences in average PTSD scores of women 
who suffered childhood sexual abuse compared to those who did not suffer from 
childhood sexual abuse.

```{r}
ggplot(data = abuse.data) +
  geom_boxplot(mapping = aes(x = csa, y = ptsd)) +
  labs(x = "Reported Childhood Sexual Abuse", y = "Post-traumatic Stress Disorder (PTSD) Scale 
       (standardized scale)",
       title = "The PTSD scores of Women",
       subtitle = "who did and did not Experience Childhood Sexual Abuse",
       caption = "Higher scores indicate higher PTSD severity") +
  scale_x_discrete(labels = c('Abused','Not Abused'))
```


***
### Question 2
#### Assigned to Genee'


***
### Question 3

Side-by-side boxplots showing the relationship of Childhood Physical Abuse 
(the covariate)  for women who suffered childhood sexual abuse to those who 
did not suffer childhood sexual abuse (the explanatory variable).

```{r}
ggplot(data = abuse.data) + 
  geom_boxplot(mapping = aes(x = csa, y = cpa)) +
  labs(x = "Reported Childhood Sexual Abuse", y = "Childhood Physical Abuse Scale 
       (standardized scale)",
       title = "The Childhood Physical Abuse scores of Women",
       subtitle = "who did and did not Experience Childhood Sexual Abuse",
       caption = "Higher scores indicate more Abuse") +
  scale_x_discrete(labels = c('Abused','Not Abused'))
```


***

### Question 4

Calculate descriptive statistics for the covariate at each level of the categorical variable.

```{r}
tapply(abuse.data$cpa, abuse.data$csa, summary)
```



***
### Question 5
#### Assigned to Meka


***
### Question 6
#### Assigned to Genee'


***
### Question 7
#### Assigned to Anna


***
### Question 8

Illustrate the relationship of the explanatory variable to the response variable after accounting for the covariate by constructing a scatterplot with separate regression lines for each level of the explanatory variable.

```{r}
library(tidyverse)
ggplot(abuse.data, aes(x = cpa, y = ptsd, color = csa)) +
  geom_point() +
  stat_smooth(method = "lm", se = FALSE) +
  labs (title = "PTSD as a Function of CPA by CSA") +
  scale_color_manual(values = c("Red", "Blue"))
```


***
### Question 9 

Construct the ANCOVA table after modeling the response variable as a function of the explanatory variable and covariate (without interaction).

```{r}
model <- abuse.data$ptsd ~ abuse.data$cpa + abuse.data$csa
model.out <- lm(model)
plot(model.out, 1)
plot(model.out, 2)
anova(model.out)
model.out
```

