---
title: "Assignment #9: Part II"
author: "Learning Group 3:Meka McCammon, Joy Li, Anna Ehrhorn, and Genee’ Glascoe"
date: "April 11, 2020"
output: html_notebook
---

***
This is a study investigated the following research question: *For women who* 
*suffered childhood physical abuse, is a difference in the average PTSD scores* 
*of women who also suffered childhood sexual abuse and those who did not suffer* 
*childhood sexual abuse, after accounting for the severity of the childhood*
*physical abuse?*

```{r include=FALSE}

library(tidyverse)

abuse.data <- read_csv("Sexual Abuse Data.csv")

abuse.data

abuse.data$csa <- factor(abuse.data$csa,
                         levels = c("Abused", "NotAbused"),
                         labels = c("Abused", "Not Abused"))
```


***
### Question 1 
#### Assigned to Meka

***
### Question 2
#### Assigned to Genee'


***
### Question 3
#### Assigned to Anna


***
### Question 4. Calculate descriptive statistics for the covariate at each level of the categorical variable.
#### Assigned to Joy
```{r}
tapply(abuse.data$cpa, abuse.data$csa, summary)
```



***
### Question 5
#### Assigned to Meka


***
### Question 6
#### Assigned to Genee'


***
### Question 7
#### Assigned to Anna


***
### Question 8. Illustrate the relationship of the explanatory variable to the response variable after accounting for the covariate by constructing a scatterplot with separate regression lines for each level of the explanatory variable.
#### Assigned to Joy

```{r}
library(tidyverse)
ggplot(abuse.data, aes(x = cpa, y = ptsd, color = csa)) +
  geom_point() +
  stat_smooth(method = "lm", se = FALSE) +
  labs (title = "PTSD as a Function of CPA by CSA") +
  scale_color_manual(values = c("Red", "Blue"))
```


***
### Question 9. Construct the ANCOVA table after modeling the response variable as a function of the explanatory variable and covariate (without interaction).
#### Assigned to Joy

```{r}
model <- abuse.data$ptsd ~ abuse.data$cpa + abuse.data$csa
model.out <- lm(model)
plot(model.out, 1)
plot(model.out, 2)
anova(model.out)
model.out
```

