---
title: "Assignment #9: Part II"
author: "Learning Group 3:Meka McCammon, Joy Li, Anna Ehrhorn, and Genee’ Glascoe"
date: "April 11, 2020"
output: html_notebook
---

***
This is a study investigated the following research question: *For women who* 
*suffered childhood physical abuse, is a difference in the average PTSD scores* 
*of women who also suffered childhood sexual abuse and those who did not suffer* 
*childhood sexual abuse, after accounting for the severity of the childhood*
*physical abuse?*

```{r include=FALSE}

library(tidyverse)

abuse.data <- read_csv("Sexual Abuse Data.csv")

abuse.data

abuse.data$csa <- factor(abuse.data$csa,
                         levels = c("Abused", "NotAbused"),
                         labels = c("Abused", "Not Abused"))
```


***
### Question 1 

Side-by-side boxplots that show differences in PTSD scores of women 
who suffered childhood sexual abuse compared to those who did not suffer from 
childhood sexual abuse.

```{r}
ggplot(data = abuse.data) +
  geom_boxplot(mapping = aes(x = csa, y = ptsd)) +
  labs(x = "Reported Childhood Sexual Abuse", y = "Post-traumatic Stress Disorder (PTSD) Scale 
       (standardized scale)",
       title = "The PTSD scores of Women",
       subtitle = "who did and did not Experience Childhood Sexual Abuse",
       caption = "Higher scores indicate higher PTSD severity") +
  scale_x_discrete(labels = c('Abused','Not Abused'))
```


***
### Question 2
#### Assigned to Genee'


***
### Question 3

Side-by-side boxplots showing the relationship of Childhood Physical Abuse 
(the covariate)  for women who suffered childhood sexual abuse to those who 
did not suffer childhood sexual abuse (the explanatory variable).

```{r}
ggplot(data = abuse.data) + 
  geom_boxplot(mapping = aes(x = csa, y = cpa)) +
  labs(x = "Reported Childhood Sexual Abuse", y = "Childhood Physical Abuse Scale 
       (standardized scale)",
       title = "The Childhood Physical Abuse scores of Women",
       subtitle = "who did and did not Experience Childhood Sexual Abuse",
       caption = "Higher scores indicate more Abuse") +
  scale_x_discrete(labels = c('Abused','Not Abused'))
```


***
### Question 4

A five-number summary and standard deviations for Childhood Phyical Abuse Scores
(the covariate) for women who suffered childhood sexual abuse to those who 
did not suffer childhood sexual abuse (the explanatory variable).

```{r}
tapply(abuse.data$cpa, abuse.data$csa, summary)

tapply(abuse.data$cpa, abuse.data$csa, sd)
```


***
### Question 5

This plot shows the difference in PTSD scores for women who were and were not 
sexually abused while taking into account childhood physical abuse, and tests 
for interaction.

```{r}
ggplot(abuse.data, aes(x = cpa, y = ptsd, color = csa))+
  stat_smooth (method = "lm", se = FALSE)+
  theme(legend.position = "right")+
  labs(x = "Childhood Sexual Abuse
       (standardized scale)",
       y = "PTSD Score
       (standardized scale)",
       title = "PTSD Scores for Women",
       subtitle = "as a function of Physical Abuse by Sexual Abuse",
       color = "Reported Childhood Sexual Abuse") +
  theme(legend.position = "bottom") +
  scale_color_discrete(labels = c('Abused','Not Abused'))
```

***
### Question 6
#### Assigned to Genee'


***
### Question 7

A Q-Q plot of the residuals calculated to confirm the condition of normal 
distribution.

```{r}
ggplot(data = abuse.data, x = csa, y = ptsd) +
  geom_qq(aes(sample = cpa)) +
  stat_qq(aes(sample = cpa)) +
  stat_qq_line(aes(sample = cpa)) +
  labs(x = "Theoretical", y = "Sample",
       title = "Q-Q Plot of Residuals when modeling for Women PTSD Scores",
       subtitle = "as a function of their reported Childhood Sexual Physical Abuse")
```


***
### Question 8

 A scatterplot illustrating the relationship of women who suffered childhood 
 sexual abuse to those who did not suffer childhood sexual abuse (the 
 explanatory variable) to their PTSD Scores (the response variable) after 
 accounting for their Childhood Physical Abuse Score (the covariate).

```{r}
library(tidyverse)
ggplot(abuse.data, aes(x = cpa, y = ptsd, color = csa)) +
  geom_point() +
  stat_smooth(method = "lm", se = FALSE) +
  labs(x = "Childhood Physical Abuse Scale 
       (standardized scale)",
       y = "Post-traumatic Stress Disorder (PTSD) Score 
       (standardized scale)",
       title = "The Childhood Physical Abuse Score by PTSD Score for Women ",
       subtitle = "who did and did not experience Childhood Sexual Abuse",
       caption = "Higher scores indicate higher severity of Abuse and/or PTSD",
       color = "Reported Childhood Sexual Abuse") +
  theme(legend.position = "bottom") +
  scale_color_discrete(labels = c('Abused','Not Abused'))
```


***
### Question 9 

The constructed ANCOVA table after modeling the women's PTSD Scores (the 
response variable) as a function for the women who suffered childhood 
 sexual abuse to those who did not suffer childhood sexual abuse (the 
 explanatory variable) and the amount of childhood physical abuse (the covariate
 - without interaction).

```{r}
model <- abuse.data$ptsd ~ abuse.data$cpa + abuse.data$csa
model.out <- lm(model)
plot(model.out, 1)
plot(model.out, 2)
anova(model.out)
model.out
```
