---
title: "Assignment #9: Part II"
author: "Learning Group 3:Meka McCammon, Joy Li, Anna Ehrhorn, and Genee’ Glascoe"
date: "April 11, 2020"
output: html_notebook
---

***
This is a study investigated the following research question: *For women who* 
*suffered childhood physical abuse, is a difference in the average PTSD scores* 
*of women who also suffered childhood sexual abuse and those who did not suffer* 
*childhood sexual abuse, after accounting for the severity of the childhood*
*physical abuse?*

```{r include=FALSE}

library(tidyverse)

abuse.data <- read_csv("Sexual Abuse Data.csv")

abuse.data

abuse.data$csa <- factor(abuse.data$csa,
                         levels = c("Abused", "NotAbused"),
                         labels = c("Abused", "Not Abused"))
```


***
### Question 1 
#### Assigned to Meka

***
### Question 2

*Calculated descriptive statistics for the response variable at each level of the categorical variable*
```{r}
tapply(abuse.data$ptsd, abuse.data$csa, summary)
```
```{r}
tapply(abuse.data$ptsd, abuse.data$csa, sd)
```


***
### Question 3
#### Assigned to Anna


***
### Question 4
#### Assigned to Joy


***
### Question 5
#### Assigned to Meka


***
### Question 6
#### Assigned to Genee'

*Calculate the predicted values and residuals when modeling the response variable as afunction of the explanatory variable and covariate (without interaction)*
```{r}
model1=lm(data=abuse.data, formula= cpa ~ ptsd)
summary(model1)
abuse.data$predicted <- predict(model1)   # Save the predicted values
abuse.data$residuals <- residuals(model1) # Save the residual values
abuse.data %>% select(cpa, predicted, residuals) %>% head()
```

*Plotted the residuals as a function of the predicted values to confirm homogeneity of variance*
```{r}
ggplot(data=abuse.data, aes(x=predicted, y=residuals, color = csa))+
  geom_point()+
  geom_smooth(method="lm")+
  labs(x = "Childhood Sexual Abuse", 
       y = "PTSD Score", 
       title = "Residuals from Childhood physcial abuse ~ PTSD model") 
```




***
### Question 7
#### Assigned to Anna


***
### Question 8
#### Assigned to Joy


***
### Question 9
#### Assigned to Joy

