---
title: "R Notebook- Joy's part"
output: html_notebook
---

### Question 4. Calculate descriptive statistics for the covariate at each level of the categorical variable.
#### Assigned to Joy
```{r}
tapply(abuse.data$cpa, abuse.data$csa, summary)
```



***
### Question 8. Illustrate the relationship of the explanatory variable to the response variable after accounting for the covariate by constructing a scatterplot with separate regression lines for each level of the explanatory variable.
#### Assigned to Joy

```{r}
library(tidyverse)
ggplot(abuse.data, aes(x = cpa, y = ptsd, color = csa)) +
  geom_point() +
  stat_smooth(method = "lm", se = FALSE) +
  labs (title = "PTSD as a Function of CPA by CSA") +
  scale_color_manual(values = c("Red", "Blue"))
```


***
### Question 9. Construct the ANCOVA table after modeling the response variable as a function of the explanatory variable and covariate (without interaction).
#### Assigned to Joy

```{r}
model <- abuse.data$ptsd ~ abuse.data$cpa + abuse.data$csa
model.out <- lm(model)
plot(model.out, 1)
plot(model.out, 2)
anova(model.out)
model.out
```